Exploration of empirical Bayes hierarchical modeling for the analysis of genome-wide association study data

### 2017-06-24 doc/manuscript/paper.tex
Population of structures

\subsection{Analysing contact count data}
- compartment analysis
- extracting some relationships between counts genomic distances etc
- fit-HiC

\subsection{3D structure inference}
- MDS
- PO
- NB

\subsubsection{Structure stability}
- Structure stability
- 
\subsubsection{Volume exclusion models}
\subsection{Integrative analysis of gene expression and 3D structure using KernelCCA}

>>>>

Let us first introduce some notations. Hi-C data can be summarized as an $n
\times n$ contact count matrix, where each row and column corresponds to a
genomic window or loci, and each entry $c_{ij}$ refers to the number of time
$i$ and $j$ have been seen interacting with one another.

Hi-C data suffers from technical and biological biases that need to be
corrected. We use ICE

\subsection{Analysing contact count data}
- compartment analysis
- extracting some relationships between counts genomic distances etc
- Extracting significant interactions using fit-HiC

Figure:
  - log-linear relationships between counts and distances.
  - significant interactions using fit-HiC ?

\subsection{3D structure inference}

A crucial step of our analysis of the \em{P. falciparum} genome relied on
visual introspection of a consensus 3D model of the genome. Being able to
quickly visualize how chromosome folded, where families of genes lied in the
3D space or whether regions where enriched helped us integrate with other
sources of data.

Briefly, we cast the problem of finding a consensus 3D structure $X \in R^{n
\times n}$ as an optimization problem, where we attempted to place each beads
in 3D so that they match as closely sa possible a predefined
``wish-distance``. We added constraints to our model based on prior knowledge,
such as the size of the nucleus, or how far apart two adjacent beads should
lie, though we showed these constraints where well satisfied even when
performing an unconstrained optimized. In this section, I will review the
inference method we used in \citet{ay:three-dimensional} as well as two newer
methods, based on well-grounded statistical method.

\subsubsection{Multidimensional scaling}

\begin{equation}
\end{equation}

\subsubsection{Modeling contact counts as a Poisson distribution}

\subsubsection{Modeling contact counts as a Negative Binomial distribution}

\subsubsection{Structure stability}
- Structure stability
- at least 100 iterations
- maybe compare results with chromSDE, PCA \& ShRec3D 
- 
\subsubsection{Volume exclusion models}

\subsection{Integrative analysis of gene expression and 3D structure using KernelCCA}

- Can we extend this to other data types? Chip-seq data available from our
review? Can the results be interpretable?
